Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-03-30 article/article.Rmd
+ big fixes

## Results
<!-- Surrogacy analysis -->
The environmental and geographic-based variables were effective surrogates for adaptive and genetic variation (Figure 1). The prioritizations generated using greater surrogate-based targets secured more genetic variation (${\chi^{2}}_{`r sub.correlation.3.ANOVA[[7]][2]`} = `r  sub.correlation.3.ANOVA[[6]][2]`$, $P  `pretty.pval(sub.correlation.3.ANOVA[[8]][2])`$). In addition, prioritizations generated using environmental targets often secured more adaptive genetic variation than prioritizations generated using geographic-based targets did neutral genetic variation (${\chi^{2}}_{`r sub.correlation.2.ANOVA[[7]][2]`} = `r  sub.correlation.2.ANOVA[[6]][2]`$, $P `r pretty.pval(sub.correlation.2.ANOVA[[8]][2])`$). Only particularly high geographic targets ($\geq 0.95$ %) were able to secure a moderate proportion of neutral variation ($\geq XXXX$ %). Overall, there was a non-linear relationship between the surrogate-based targets used to generate the prioritizations and the proportion of genetic variation they secured.

@@

The inclusion of surrogate-based targets caused an improvement in the proportion of neutral variation secured in a prioritization (Figure 3). Specifically, the proportion of genetic variation secured by the prioritizations differed depending on the type of genetic variation measured (${\chi^{2}}_{`r sub.scenario.6.ANOVA[[7]][2]`} = `r  sub.scenario.6.ANOVA[[6]][2]`$, $P  `pretty.pval(sub.scenario.6.ANOVA[[8]][2])`$) and combination of targets used to generate the prioritizations (${\chi^{2}}_{`r sub.scenario.7.ANOVA[[7]][2]`} = `r  sub.scenario.7.ANOVA[[6]][2]`$, $P  `pretty.pval(sub.scenario.7.ANOVA[[8]][2])`$). No significant differences were found among the single-species, multi-species, and multi-species with cost contexts (${\chi^{2}}_{`r sub.scenario.5.ANOVA[[7]][2]`} = `r  sub.scenario.5.ANOVA[[6]][2]`$, $P `pretty.pval(sub.scenario.5.ANOVA[[8]][2])`$).

>>>>

## Results
<!-- Surrogacy analysis -->
The environmental and geographic-based variables were effective surrogates for adaptive and genetic variation (Figure 1). The prioritizations generated using greater surrogate-based targets secured more genetic variation (XXXX). In addition, prioritizations generated using environmental targets often secured more adaptive genetic variation than prioritizations generated using geographic-based targets did neutral genetic variation (XXXX). Only particularly high geographic targets ($\geq 0.95$ %) were able to secure a moderate proportion of neutral variation ($\geq XXXX$ %). Overall, there was a non-linear relationship between the surrogate-based targets used to generate the prioritizations and the proportion of genetic variation they secured.

@@

The inclusion of surrogate-based targets caused an improvement in the proportion of neutral variation secured in a prioritization (Figure 3). Specifically, the proportion of genetic variation secured by the prioritizations differed depending on the type of genetic variation measured (XXXX) and combination of targets used to generate the prioritizations (XXXX). No significant differences were found among the single-species, multi-species, and multi-species with cost contexts (XXXX).

### 2016-03-30 article/figures.Rmd
+ big fixes

		Prioritization=revalue(Prioritization, c('Amount'='Amount\ntargets', 'Surrogate'='Amount & surrogate\ntargets', 'Genetic'='Amount & genetic\ntargets')),
		Prioritization=factor(as.character(Prioritization), levels=c('Amount\ntargets', 'Amount & surrogate\ntargets', 'Amount & genetic\ntargets')),

@@

# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=value),
		data=scenario.DF) +
		geom_boxplot(position=position_dodge(0.9)) +
		geom_abline(
			intercept=rapr.params.LST[[MODE]]$scenario.analysis$genetic.target,
			slope=0, color='red',linetype='dashed') +
		geom_text(aes(x=Prioritisation, y=letter.height, label=letter),
			data=scenario.PDF, position=position_dodge(0.9)) +
		geom_text(aes(x=0.5, y=1.075, label=panel.letter),
			data=scenario.PDF) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white'),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
		facet_grid(Context ~ Metric)
})
```

>>>>

		Prioritization=revalue(Prioritization, c('Amount'='Amount targets', 'Surrogate'='Amount & surrogate\ntargets', 'Genetic'='Amount & genetic\ntargets')),
		Prioritization=factor(as.character(Prioritization), levels=c('Amount targets', 'Amount & surrogate\ntargets', 'Amount & genetic\ntargets')),

@@

# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=value),
		data=scenario.DF) +
		geom_boxplot(position=position_dodge(0.9)) +
		geom_abline(
			intercept=rapr.params.LST[[MODE]]$scenario.analysis$genetic.target,
			slope=0, color='red',linetype='dashed') +
		geom_text(aes(x=Prioritisation, y=letter.height, label=letter),
			data=scenario.PDF, position=position_dodge(0.9)) +
		geom_text(aes(x=0.6, y=1.09, label=panel.letter),
			data=scenario.PDF) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white'),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
		facet_grid(Context ~ Metric)
})
```
